---
title: "Wrangle Glasshouse data"
author: "P. Melloy"
date: "13/03/2020"
output: html_document
---
```{r import_libraries}
library("tidyverse")
library("skimr")
```

If you are using this data please reference the original work and the data. BibTex files located in the `ref/` directory.

## Import data
First lets import the visual assessment data from figshare.
```{r import_symptom&phenology_data}
dat_fcr <- read_csv("https://ndownloader.figshare.com/files/21990357")

skim(dat_fcr)
```

### Explaination of data

   1. ID:     Relates to a single plant in a single pot.  
   2. cul:    Wheat genotype, or commercial cultivar name.  
   3. inoc:   When or if the pot/plant was inoculated; 
      i) None - noninoculated  
      ii) 21 days - inoculated at 21 days after planting  
      iii) Late Tillering - inoculated late in the the wheat maturity stage 'Tillering' prior to stem elongation.  
   4. rep:    Biological replicates
   5. sT:     Sampling stage, refers to when the plant was destructivley sampled for analysis.  
      i) 1 - Initiating of stem elongation, zadocks maturity stage XXX
      i) 2 - Flowering, zadocks maturity stage XXX
      i) 3 - Soft dough, zadocks maturity stage XXX
      i) 4 - Crop maturity, zadocks maturity stage XXX
   

Lets also import the relative fungal biomass data from figshare.
```{r import_fungalBiomass_data}
dat_rb <- read_csv("https://ndownloader.figshare.com/files/21990354")

skim(dat_rb)
```





   