---
title: "Wrangle Glasshouse data"
author: "P. Melloy"
date: "13/03/2020"
output: html_document
---
```{r import_libraries}
library("tidyverse")

```


## Import data
This needs to be changed so it imports from figshare
```{r import_data}
datFCR <- read_csv("data/1301_FCRatElevatedCO2_Glasshouse_figshare_RAW_PM.csv")

datFCR
```

### Explaination of data

   1. ID:     Relates to a single plant in a single pot.  
   2. cul:    Wheat genotype, or commercial cultivar name.  
   3. inoc:   When or if the pot/plant was inoculated; 
      i) None - noninoculated  
      ii) 21 days - inoculated at 21 days after planting  
      iii) Late Tillering - inoculated late in the the wheat maturity stage 'Tillering' prior to stem elongation.  
   4. rep:    Biological replicates
   5. sT:     Sampling stage, refers to when the plant was destructivley sampled for analysis.  
      i) 1 - Initiating of stem elongation, zadocks maturity stage XXX
      i) 2 - Flowering, zadocks maturity stage XXX
      i) 3 - Soft dough, zadocks maturity stage XXX
      i) 4 - Crop maturity, zadocks maturity stage XXX
   
   